Use of asynchronous circuits and leakiness in modeling biological circuit of the Caulobacter Crescentus cell cycle

### 2017-03-10 asyncleakyn.tex
finished adding to dynamic memory

\title{Use of asynchronous circuits and leakiness in modeling biological circuit of the Caulobacter Crescentus cell cycle}
\author{Zoey Zhou}
\date{\today}  
\usepackage{graphicx}
\graphicspath{ {c:/Users/cuizy/Downloads/} }
\begin{document}

@@

\section{Static and Dynamic Memory}

@@

\includegraphics{srlatch}

@@

%Can insert a picture here too

@@

Using standard parameter values, it is possible to have the hold times to be longer than the set reset times and so for short periods of time, this element can be considered as a set-reset memory element.  Thus we can abstract these biological motifs as a series of static and dynamic memories connected to each other.

>>>>

\title{Use of asynchronous circuits and leakiness in modeling biological circuit of the Caulobacter Crescentus cell cycle}
\author{Zoey Zhou}
\date{\today}  
\usepackage{graphicx}
\graphicspath{ {c:/Users/cuizy/Downloads/} }
\usepackage{amsmath}
\begin{document}

@@

\section{Dynamic Memory}

@@

\begin{tabular}{|p{1.5cm}|p{1.5cm}|p{1.5cm}|p{2cm}| } 
 \hline
\textbf{S} & \textbf{R} & \textbf{Qnext} & \textbf{Action} \\
\hline
1 & 0 & 1 & set \\
\hline
0 & 1 & 0 & reset \\ 
\hline
0 & 0 & Q & hold state \\ 
\hline
1 & 1 & X & not allowed\\ 
\hline
\end{tabular}

@@

%insert some graph here

@@

We check the function of the gcrA gene module against these equations.  We use parameter values that were previously determined for the ODE model from both experimental data and reasonable approximations based on these experiments.  

\begin{tabular}{|p{1.8cm}|p{1cm}|p{1cm}|p{7cm}| } 
 \hline
\textbf{Parameter} & \textbf{Value} & \textbf{Units} & \textbf{Parameter explanation} \\
\hline
$\lambda_{sw}$ & 10.5 & min & GcrA half-life in swarmer \\ 
\hline
$\lambda_{st}$ & 42 & min & GcrA half-life in stalked \\ 
\hline
$issw$ & 0 or 1 & & boolean value where 1 indicates cell is in the swarmer state \\
\hline
$p_{gcrA}$ & 2.2 & nM/s & Maximum synthesis rate of GcrA from the promoter \\ 
\hline
$c_{HalfCtrA}$ & 1760 & nM & Concentration of CtrA~P that yields half of the maximum expression of CtrA-regulated genes\\
\hline
$c_{HalfDef}$ & 660 & nM & Default concentration of transciption factors ie. gcrA that yields half of the maximum expression of target genes\\
\hline
\end{tabular}

\end{center}
The equation for the ODE of just the gcrA gene module is:
\[
\begin{split}
\frac{d gcrA}{d t}=\frac{2.2}{(1+(\frac{660}{dnaA})^2)\cdot (1+(\frac{ctrAP}{1760})^2)}-gcrA\cdot (\frac{log(2)}{60\cdot 42} \\
+(issw)\cdot \frac{log(2)}{60\cdot 10.5})
\end{split}
\]
And the equation for the steady state is:
\[gcrA_{ss}=\frac{2.2}{(1+(\frac{660}{dnaA})^2)\cdot (1+(\frac{ctrAP}{1760})^2)\cdot (\frac{log(2)}{60\cdot 42}
+(issw)\cdot \frac{log(2)}{60\cdot 10.5})}
\]
The various input and output thresholds that we use are:
\[in_{min0}: dnaA=0, ctrAP=1760  \Rightarrow g(in_{min0})=0, g'(in_{min0})=0
\]
\[in_{max0}: dnaA=150, ctrAP=0  \Rightarrow g(in_{max0})=267, g'(in_{max0})=393
\]
\[in_{min1}: dnaA=660, ctrAP=1760  \Rightarrow g(in_{min1})=2666 %wouldn't this be a pareto frontier thing?
\]
\[in_{max1}: dnaA=1000, ctrAP=0  \Rightarrow g(in_{max1})=3800
\]
\[fanout_0=600
\]
\[fanout_1=1100
\]
With these set of parameters and thresholds the set rest and hold times are:
\[\Delta t_{set}=1934.23749
\]
\[\Delta t_{reset}=1716.50821
\]
\[\Delta t_{hold0}= inf
\]
\[\Delta t_{hold1}=3218.61297
\]
The minimum hold times here are longer than the maximum set reset times and so for short periods of time, this element can be considered as a set-reset memory element.  Since these are the worst possible bounds, in practice set reset times would be shorter and the hold times would be even longer.  Thus we can abstract these biological motifs as a series of dynamic memories connected to each other.
